Development and assessment of automated forest road projection methods using performance metrics relevant for wildlife

### 2024-06-12 analysis/paper/paper.Rmd
very minor edits

Road network data was obtained by combining the digital road atlas [@data_bc_digital_2021] and forest tenure road [@british_columbia_ministry_of_forests_lands_natural_resource_operations_and_rural_development_forest_2021] data sets for British Columbia. We removed all roads from the digital road atlas that were within 50 m of forest tenure roads to avoid duplication. To obtain a starting point for projections we filtered out forest tenure roads with an award date greater than 1990, and assumed everything in the digital road atlas was built before 1990. Cutblock information was obtained from the Harvest Areas of BC (Consolidated Cutblocks) dataset [@government_of_british_columbia_harvested_2021], compiled from provincial Forest Cover, the RESULTS Reporting system, Forest Tenure applications, and satellite imagery using change detection processes. We used cutblocks harvested after 1990 as as targets for the projections, and removed cutblocks that that do not contain observed roads to reduce errors associated with open areas that have been misidentified as cutblocks.

@@

Examination of spatial mismatch between observed and projected roads also highlighted errors in our input data that are not unique to our study area; there is considerable variation in the consistency and accuracy of available resource road information across Canada and elsewhere [@poley_identifying_2022; @british_columbia_ministry_of_forests_lands_natural_resource_operations_and_rural_development_resource_nodate] that users should keep in mind interpreting discrepancies between observed and projected road networks.

>>>>

Road network data was obtained by combining the digital road atlas [@data_bc_digital_2021] and forest tenure road [@british_columbia_ministry_of_forests_lands_natural_resource_operations_and_rural_development_forest_2021] data sets for British Columbia. We removed all roads from the digital road atlas that were within 50 m of forest tenure roads to avoid duplication. To obtain a starting point for projections we filtered out forest tenure roads with an award date greater than 1990, and assumed everything in the digital road atlas was built before 1990. Cutblock information was obtained from the Harvest Areas of BC (Consolidated Cutblocks) dataset [@government_of_british_columbia_harvested_2021], compiled from provincial Forest Cover, the RESULTS Reporting system, Forest Tenure applications, and satellite imagery using change detection processes. We used cutblocks harvested after 1990 as targets for the projections, and removed cutblocks that do not contain observed roads to reduce errors associated with open areas that have been misidentified as cutblocks.

@@

Examination of spatial mismatch between observed and projected roads also highlighted errors in our input data that are not unique to our study area; there is considerable variation in the consistency and accuracy of available resource road information across Canada and elsewhere [@poley_identifying_2022; @british_columbia_ministry_of_forests_lands_natural_resource_operations_and_rural_development_resource_nodate] that users should keep in mind when interpreting discrepancies between observed and projected road networks.
